Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
minor corrections

As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem. We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system. The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$. Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step. Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$). Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation. 

>>>>

As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem. We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system. The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$. Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step. Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$). Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation. 
